\begin{description}
\item [{Cash~Lane}] A cash lane is operated by a cashier, who accepts cash
payments as well as credit cards. When a cashier operates a credit card
lane, it becomes a cash lane.

\item [{Cashier}] A cashier operates a cash lane and accepts cash payment
in exchange for single tickets.

\item [{Customer}] The customer is the driver of a vehicle.

\item [{Credit~Card~Lane}] In a credit card lane, the customer can use their
credit card to purchase a single ticket.

\item [{Enterprise}] The company which control these sections of the motorway.

\item [{Enterprise~Manager}] The manager who is in charge of all the toll stations.

\item [{Enterprise~Server}] The enterprise server is the main connection point of all the subsystems.

\item [{Express~Lane}] An express lane will automatically admit passage
to vehicles equipped with a toll tag. The vehicle will be registered
as having passed through the lane at the given time.

\item [{Normal~Lane}] A normal lane is an umbrella term for non-express lanes.

\item [{Rate}] The price to pay for a certain vehicle type for certain ticket/tag type.

\item [{Single ticket}] A ticket issued to a customer when checking in at a normal toll lane. It is valid for 24 hours or until used to check out.

\item [{Station~Manager}] The manager who is in charge of a single toll station.

\item [{Station~Server}] Each toll station has a Staion Server which handles communications from the toll lanes to the rest of the system.

\item [{Statistical~Report}] Each toll station records which vehicles
purchased single tickets and used toll tags, along with the type of
the vehicle. A statistical report is a write-out of this information
for a given time period.





\item [{Toll~tag}] A toll tag is a physical device which will admit passage
through an express lane when equipped on a vehicle. Toll tags need
to be ordered by customers, and can only be used by one vehicle. The
toll system automatically computes the fare of the vehicle based on
the distance travelled between check in and check out.

\item [{Toll~Station}] A toll station is a collection of toll lanes. A
station manager is connected to every toll station and can view \emph{statistical
reports}, as well as view and modify customer data.







\end{description}
