\subsection {Domain Analysis}

\subsubsection {Glossary}

\begin{description}
\item [{Toll~tag}] A toll tag is a physical device which will admit passage
through an express lane when equipped on a vehicle. Toll tags need
to be ordered by customers, and can only be used by one vehicle. The
toll system automatically computes the fare of the vehicle based on
the distance travelled between check in and check out.

\item [{Single~ticket}] Single tickets can be purchased in a cash or credit
card lane, and are valid for 24 hours.

\item [{Toll~Station}] A toll station is a collection of toll lanes. A
station manager is connected to every toll station and can view \emph{statistical
reports}, as well as view and modify customer data.

\item [{Statistical~Report}] Each toll station records which vehicles
purchased single tickets and used toll tags, along with the type of
the vehicle. A statistical report is a writeout of this information
for a given time period.

\item [{Express~Lane}] An express lane will automatically admit passage
to vehicles equipped with a toll tag. The vehicle will be registered
as having passed through the lane at the given time.

\item [{Credit~Card~Lane}] In a credit card lane, the user can use their
credit card to purchase a single ticket.

\item [{Cash~Lane}] A cash lane is manned by a cashier, who accepts cash
payments as well as credit cards. When a cashier mans a credit card
lane, it becomes a cash lane.

\item [{Cashier}] A cashier operates a cash lane and accepts cash payment
in exchange for single tickets.

\item [{Customer}]~

\item [{Rate}]~

\item [{Administrative~Operations}]~
\end{description}

\subsubsection {Use Case Diagram}

\subsection{Functional Requirements}

\subsubsection{Activity Diagram}

\subsubsection{Detailed Use Case}

\textit {Name: } Check in single ticket

\textit {Description: } A customer in a vehicle enters the toll lane and buys a single ticket.

\textit {Actors: } A customer and a cashier.

\textit {Preconditions: }  The customer is in a cash lane

\textit{Main Scenario: }

\begin{enumerate}
	\item The cashier identifies themself as being a cashier by using the touchscreen
	\item The cashier selects the customers vehicle type on the touch screen.
	\item The price for the relevant vehicle type is displayed on the screen.
	\item The cashier opens the cash register
	\item The cashier opens the cash register
	\item The ticket is printed to the customer
	\item The barrier opens
	\item The barrier closes when the vehicle has passed through
\end{enumerate}

\textit{Alternative Scenarios: }
\begin{enumerate}
	\item The cashier is not present, or the customer wants to pay with their credit card
		\begin{enumerate}
			\item The customer selects his vehicle type
			\item The price for a single ticket is presented to the customer
			\item The customer pays by using the card reader
			\item The card reader processes the payment successfully
			\item The ticket is printed
			\item The barrier opens
			\item The barrier closes when the vehicle has passed through
		\end{enumerate}
		
	\item The payment does not succeed
		\begin{enumerate}
			\item Restart the scenario.
		\end{enumerate}

 \end{enumerate} 
 
 \textit{Note :} We assume that the customer hands over the correct amount of money to the cashier, and that the cashier deposits the money.


\subsection{Non-Functional Requirements}