
\textit {Description: } A customer in a vehicle enters the toll lane and buys a single ticket.

\textit {Actors: } A customer and a cashier.

\textit {Preconditions: }  The customer is in a cash lane.

\textit{Main Scenario: }

\begin{enumerate}
	\item The cashier selects the customer's vehicle type.
	\item The system displays the price for that vehicle type.
	\item The cashier puts the money in the cash register.
	\item The system prints the ticket.
	\item The system opens the barrier.
	\item The customer leaves the toll lane.
	\item The system closes the barrier.
\end{enumerate}

\textit{Alternative Scenarios: }
\begin{enumerate}
	\item The cashier is not present, the cash payment fails, or the customer wants to pay with their credit card.
		\begin{enumerate}
			\item The customer selects his vehicle type.
			\item The system presents the price for a single ticket.
			\item The customer pays using the card reader.
			\item The system processes the payment successfully.
			\item The system prints the ticket.
			\item The system opens the barrier.
			\item The customer leaves the toll lane.
			\item The system closes the barrier.
		\end{enumerate}
		
	\item The credit card payment does not succeed. 
		\begin{enumerate}
			\item Restart the scenario.
		\end{enumerate}

 \end{enumerate} 
 
 \textit{Note:} 
 \begin{enumerate}
 \item We assume that the customer hands over the correct amount of money to the cashier, and that the cashier deposits the money.
 \item The cash payment fails if the customer does not have enough money.
 \end{enumerate}